Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-20 egpaper_supp.tex
8 pages

\section{PASCAL3D+}

It this section, we provide qualitative examples and plots for the experiment
``Enriching Existing Detection''. To recapitulate, we used object detection
bounding boxes from state-of-the-art detectors \cite{Girshick14, Pepik12} and
enrich bounding boxes with 2D-3D registration and continuous viewpoint
estimation. We present detection average precision, average viewpoint
precision, viewpoint confusion matrix and mean precision in pose estimation
results on Fig.~\ref{fig:pascal_ap}.

We followed the evaluation criteria of \cite{Xiang14} for detection and
viewpoint estimation.

In this experiment, we used R-CNN\cite{Girshick14} for detection bounding box
proposals and our system produces accurate 2D-3D matching on the proposal
regions. We used $15\%$ context (extend the proposal region by $15\%$ on the
top, right, left and bottom). We run our pipeline on PASCAL3D+
dataset\cite{Xiang14} with fine-tuning stage.

If our method fails to estimate viewpoint (confidence score is below 45), it
estimates 0 azimuth, 0 elevation, 0 yaw. Note that for all categories and
different number of viewpoints, our method has difficulty discerning frontal
view and back view.

\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+ dataset. On the left, we
  present average precision curve (red) average viewpoint precision curve
  (green). On the right, we present confusion matrix and mean precision in pose
  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}

We put qualitative results on Fig.~\ref{fig:pascal3d_car_good} to
Fig.~\ref{fig:pascal3d_bicycle_bad}.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation result on PASCAL3D+ dataset
  car category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_car_good}
\end{figure*}

@@

\section{Fine Tuning}

In this section, we give qualitative examples of before and after the
fine-tuning stage on Fig.~\ref{tuning}.

See section ``Pose Fine-Tuning via MCMC'' for more detail.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{From left to right, original images, initial pose estimations and
fine-tuned result. The numbers, from the left, indicate detection confidence
and intersection over union respectively.} 
  \label{fig:tuning}
\end{figure*}

\clearpage
\clearpage
{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

>>>>

\section{Enriching Existing Detections}
%
It this section, we provide qualitative examples and plots for the experiment
``Enriching Existing Detections'' (Sect.~6.3 in the main paper).

To recapitulate, we enrich object detection bounding boxes from
a state-of-the-art detector (R-CNN~\cite{Girshick14}) with 2D-3D
registration and continuous viewpoint estimation. We present detection
average precision, average viewpoint precision, viewpoint confusion
matrix and mean precision in pose estimation results in
Fig.~\ref{fig:pascal_ap}, following the evaluation criteria
of~\cite{Xiang14} for detection and viewpoint
estimation. Fig.~\ref{fig:pascal3d_car_good} to
Fig.~\ref{fig:pascal3d_bicycle_bad} give qualitative results.
%
%In this experiment, we use R-CNN\cite{Girshick14} for detection bounding box
%proposals and our system produces accurate 2D-3D matching on the proposal
%regions.

We use $15\%$ context (extending the proposal region by $15\%$ on the
top, right, left, and bottom). We run our pipeline on the
PASCAL3D+~\cite{Xiang14} dataset, including our fine-tuning stage.
%
%If our method fails to estimate viewpoint (confidence score is below
%45), it
If our method fails to estimate viewpoint (confidence score is below a
threshold), it outputs 0 azimuth, 0 elevation, 0 yaw. Note that for
both categories and different numbers of viewpoints, our method has
difficulty distinguishing front and back views, but yields little
confusion between neighboring views. The failure cases given in
Fig.~\ref{fig:pascal3d_car_bad} and
Fig.~\ref{fig:pascal3d_bicycle_bad} are mostly caused by truncation,
occlusion, and unusual object shape.
%
\begin{figure*}[h]
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn8_crop.png}\\
    (a) Car, 4 views&
    (b) Car, 8 views\\
  \includegraphics[width=0.45\linewidth]{car_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{car_cnn24_crop.png}\\
    (c) Car, 16 views&
    (d) Car, 24 views\\
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn4_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn8_crop.png}\\
    (e) Bicycle, 4 views&
    (j) Bicycle, 8 views\\  
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn16_crop.png}&
  \includegraphics[width=0.45\linewidth]{supp/bicycle_cnn24_crop.png}\\
    (g) Bicycle, 16 views&
    (h) Bicycle, 24 views\\
  \end{tabular}
  \caption{Detection and pose estimation on PASCAL3D+ dataset. On the left, we
  present average precision curve (red) average viewpoint precision curve
  (green). On the right, we present confusion matrix and mean precision in pose
  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
  $n-1$ is front-left for number of viewpoints $n$.}
  \label{fig:pascal_ap}
\end{figure*}
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
  \caption{Successful detection and pose estimation result on PASCAL3D+ dataset
  car category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_car_good}
\end{figure*}

@@

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{From left to right, original images, initial pose estimations and
fine-tuned result. The numbers, from the left, indicate detection confidence
and intersection over union respectively.} 
  \label{fig:tuning}
\end{figure*}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}
